Design of Blur Invariant Fiducial for Low Cost Quadcopter

### 2014-02-26 ECCV/paper.tex
1. Changed output images 2. Added workflow, teaser

\section{Related Work}

Our problem may be classified broadly in two areas; fiducial markers and
tracking. So, we will briefly discuss work done in both areas.
\begin{figure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  Intersense\cite{NaimarkF02}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}  
 \centering 
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit\cite{ARToolkit02}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\cite{Fiala05}
 \end{subfigure} 
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.png}
  Pi-Tag\cite{Pitag13}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{newconcentric_01.pdf}  
  Our Fiducial  
 \end{subfigure}
 \caption{Various Fiducial Marker Designs}
 \label{fig:previous_work}  
\end{figure}

@@

\section{Design of Fiducial}
Inspired from Circular Data Matrix\cite{NaimarkF02} we have designed a fiducial
that may be thought of as a binary code.  It contains concentric white rings of
equal widths on a black background with a blurred border. The outermost and
innermost rings represent the start and end of the code and is embedded in the
fiducial; these are not considered part of the code itself. The binary code is
represented by the presence (or absence) of rings between ``marker'' rings.

@@

\section{Fiducial Detection Algorithm}
Our fiducial detection strategy is different from \cite{NaimarkF02} and works
under significant amount of blur. Our algorithm is based on the fact that there
is no blur in the direction perpendicular to the direction of the motion.
Overall flow of fiducial detection algorithm can be summarised as follows:
\begin{itemize}
  \item Apply Gabor Filter on input image
  \item Find Connected components in Gabor output
  \item Cluster the connected components in bounding box
  \item Detect code in the bounding box
  \begin{itemize}
    \item Run PCA on Gabor output in bounding box
    \item Find intensity profile along first principal component passing through
    centroid
    \item If there are less than four black to white transitions in the
    intensity profile, ignore the bouding box
    \item Otherwise, classify the detected code by the classifer trained on
    standards.
  \end{itemize}
\end{itemize}

>>>>

\begin{figure}
\includegraphics[width=\linewidth]{teaser.pdf}
\caption{Figure showing experimental setup and comparison of
output of ALVAR\cite{alvar} (for detecting ARTag) versus output of our
algorithm, in normal and blurred scene}
\end{figure}

\section{Related Work}
Our problem may be classified broadly in two areas; fiducial markers and
tracking. So, we will briefly discuss work done in both areas.
\begin{figure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  Intersense\cite{NaimarkF02}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}  
 \centering 
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit\cite{ARToolkit02}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\cite{Fiala05}
 \end{subfigure} 
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.png}
  Pi-Tag\cite{Pitag13}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{newconcentric_01.pdf}  
  Our Fiducial  
 \end{subfigure}
 \caption{Various Fiducial Marker Designs}
 \label{fig:previous_work}  
\end{figure}

@@

\section{Design of Fiducial}

Inspired from Circular Data Matrix\cite{NaimarkF02} we have designed a fiducial
that may be thought of as a binary code.  It contains concentric white rings of
equal widths on a black background with a blurred border. The outermost and
innermost rings represent the start and end of the code and is embedded in the
fiducial; these are not considered part of the code itself. The binary code is
represented by the presence (or absence) of rings between ``marker'' rings.

@@

\section{Fiducial Detection Algorithm}
\begin{figure}
\includegraphics[width=\linewidth]{overall_flow.pdf}
\caption{Overall Workflow}
\end{figure}
Our fiducial detection strategy is different from \cite{NaimarkF02} and works
under significant amount of blur. Our algorithm is based on the fact that there
is no blur in the direction perpendicular to the direction of the motion.
Overall flow of fiducial detection algorithm can be summarised as follows:
\begin{itemize}
  \item Apply Gabor Filter on input image
  \item Find Connected components in Gabor output
  \item Cluster the connected components in bounding box
  \item Detect code in the bounding box
  \begin{itemize}
    \item Run PCA on Gabor output in bounding box
    \item Find intensity profile along first principal component passing through
    centroid
    \item If there are less than four black to white transitions in the
    intensity profile, ignore the bouding box
    \item Otherwise, classify the detected code by the classifer trained on
    standards.
  \end{itemize}
\end{itemize}
